Correlations between gender and research topics at three major archaeology conferences

### 2022-02-08 analysis/paper/paper.Rmd
add figure captions

---
title: "Correlations between gender and research topics at three major archaeology conferences"
author:
  - Yichun Chen:
      email: yichun33@uw.edu
      institute: [UofO]
      correspondence: true
  - Ben Marwick:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

Gender bias and imbalance has been a concern in archaeology since the earliest discussions of the social structure of the discipline [@Gero1983]. According to the American Anthropological Association's (AAA) _AnthroGuide_, there is a growing number of women participating in anthropology's graduate programs. For example, in the 2012-2013 school year, women consist of 64% of graduate students in anthropology programs and 65% of students that completed an anthropology doctoral degrees were women, whereas in 1972 32% of PhD are granted to women and 59% in 1995 [@bardolph2014critical]. Although women slightly outnumber men in anthropology graduate programs, previous work has shown substantial gender imbalances in publication practices in archaeology where men greatly outnumber women, especially as first authors in peer reviewed journal articles [@bardolph2014critical]. One of the first studies of this imbalance in publication practices is @bardolph2014critical, who looked at 7,381 members of the Society of American Archaeology and found 53% men and 47% women. She also looked at 1,601 articles published during 1990-2013 in five high-visibility archaeology journals and found a range of proportions of women to men authors of 0.32-0.73, with three of the five journals having a proportion of <0.5.

@@

Another similar imbalance can be seen in terms of the authorship of articles or papers written. For example, for the authorship of the first authors of 1,104 articles published in the _Journal of Field Archaeology_ during 1974–2018, 72% of them are men [@heath2020guest]. @heath2020guest investigates the possibility that the gender gap in authorship is due to due to sexism in the peer review process. Out of 830 instances of peer review for where both the reviewer’s gender and the first author's gender could be determined, neither the first author’s gender, the reviewer’s gender, nor the combination of the two had a significant effect on the reviewer's recommendation.

@fulkerson2019dominates collected data on author's gender and occupational affiliation in peer reviewed journals (_American Antiquity_ (AQ), _Advances in Archaeological Practice_ (AAP), _Journal of California and Great Basin Anthropology_ (JCGBA), and _California Archaeology_ (CA)) and some non-peer-reviewed venues (the _SAA Archaeological Record_ (SAA Record) and the SCA _Proceedings_). Among the 5,010 authors of 2,445 articles in their sample, 27.1% of first/single authors of peer-reviewed journal articles are women, and 72.9% are men. The gender gap is less pronounced in the non-peer-reviewed venues with women accounting for 40.8% of lead authors in 517 articles.

@@

When looking at gender ratios among the membership in Society for California Archaeology from 1967 to 2016, @tushingham2017peer report a trend of women increasingly maintaining their society membership they remain underrepresented in peer-reviewed journals. @tushingham2017peer examined authorship gender trends in 1,599 papers in three journals, _Journal of California and Great Basin Anthropology/Journal of California Archaeology_ (JCGBA/JCA), _California Archaeology_ (CA) and a non-peer reviewed _Proceedings_ of the Society for California Archaeology (PSCA). In a total of 2,617 authors, 844 (32.3%) were women, 1,762 (67.3%) were men, and 11 (0.4%) were gender unknown/ambiguous [@tushingham2017peer]. They found significant increases in the proportion of female lead authors over time in JCGBA/JCA and PSCA, but not in CA, perhaps because of the shorter publishing period for this journal [@tushingham2017peer]. This similar trend of a gender gap in archaeology can also be seen in women's pay [@vanderwarker2018ucsb]. In the University of California, Santa Barbara Gender Equity Project,@vanderwarker2018uscb report an imbalance in pay rates, for example, women make a greater proportion of people paid less \$60,000 and men outnumber women in salary brackets greater than \$60,000. [@vanderwarker2018uscb].

@@

```{r}
library(here)
# column names should be:
# session, FirstName, AbstractTitle

@@

A structural topic model (STM) allows us to include, alongside the typical topic modeling process, other document-level metadata to analyse covariance between topics and metadata [@roberts2019package]. Covariates of interest can be included into the prior distributions for document-topic proportions and topic-word distributions using a standard regression model [@roberts2014structural]. This means that we can examine the relationship between the topics and document-level variables of interest. In our case, we computed the relationship between the inferred the gender of the first-named presenter for each presentation, and the distribution of topics in that person's presentation. After we observed the topics for each presentation, we then generated a regression where the topic is the outcome variable, and gender is the explanatory variable. This regression gives us insights into whether there are non-random relationships between the inferred gender of an archaeologist and the topics of their presentation. Our data visualisations represent the estimated marginal effect (the x-axis values) of gender on each topic (distributed on the y-axis). Our visualisations show point estimates and 95% confidence intervals for each topic, and we interpret a statistically significant gender effect on the distribution of a topic when the 95% confidence interval does not includ also (also coloured red in our figures).

# Reproducibility and open source materials {-}

@@

```{r, eval=FALSE}

@@

```{r}
# get plots
library(tidyverse)

SAA_stm_topic_number <-
  SAA18_stm_plot$model$settings$dim$K
SAA_stm_topic_number_significant_covary <- 
  nrow(layer_data(SAA18_stm_plot$plot, 3))

CAA_stm_topic_number <-
  CAA18_stm_plot$model$settings$dim$K
CAA_stm_topic_number_significant_covary <- 
  nrow(layer_data(CAA18_stm_plot$plot, 3))

EAA_stm_topic_number <-
  EAA18_stm_plot$model$settings$dim$K
EAA_stm_topic_number_significant_covary <- 
  nrow(layer_data(EAA18_stm_plot$plot, 3))
```

@@

```{r}
# some basic visualisations to show the data
list_confs <- 
  list(SAA18_gender %>% 
              mutate(session = as.character(session)),
       CAA18_gender,
       EAA18_gender %>% 
              mutate(session = as.character(session))
       )

@@

all_conf_tbl <- 
  bind_rows(list_confs,
            .id = "conf")

# how many papers per conf?
ggplot(all_conf_tbl) +
  aes(conf,
      fill = gender) +
  geom_bar(position = "dodge") +
  theme_minimal(base_size = 16) +
  theme(legend.position = c(.2,.60)) +
  labs(x = "", 
       y = "number of papers presented in 2018")
```

Overall we see similar women-to-men ratios for the SAA (`r female_to_male_SAA18`) and EAA (`r female_to_male_EAA18`), but much lower for the CAA (`r female_to_male_CAA18`). Even before we look into the gender preferences for specific topics within each conference, we already have a hint that computational topics may be less preferred by women than by men.

In the SAA data we found a total of `r prettyNum(SAA18_row, big.mark = ",")` presentations. Of these we could identify the first-named authors of `r count_gendered_SAA18` (`r perc_gendered_SAA18`%) presentations as either men (n=`r male_count_SAA18`) or women (n=`r female_count_SAA18`). In the SAA presentations we identified the optimum number of topics as `r SAA_stm_topic_number`, with `r SAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. Eight of these topics were associated with men, and nine topics associated with women. One of the main difference that we can see between the topics of the genders are the locations that the presenters are interested in. Topics associated more with women include bioarchaeology, cemeteries, burials, shells, and ceramics. Topics associated more with men include survey and landscape archaeology, geoarchaeology, rituals, and regional studies. Women are more likely to work on locations such as Mesoamerica, Arizona and national parks, while men are more likely to present on topics about the Great Lakes, and Honduras.

For the EAA data we have `r prettyNum(EAA18_row, big.mark = ",")` presentations, and `r count_gendered_EAA18` (`r perc_gendered_EAA18`%) where the first author could be classified as either a man (n=`r male_count_EAA18`) or woman (n=`r female_count_EAA18`). For EAA we generated a total of `r EAA_stm_topic_number` topics, with `r EAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. Seven of these topics were associated with men, and nine topics associated with women. Although topics significantly associated with men and women both include the word "Mediterranean", women seem to be focusing more on the western Mediterranean while men seems to be focusing on the northern Mediterranean. Topics associated more with women include burials, graves, museums, animals, diet, and ritual. Topics associated more with men include geoarchaeology, architecture, and towns.

For the CAA meeting we have `r prettyNum(CAA18_row, big.mark = ",")` presentations, and `r count_gendered_CAA18` (`r perc_gendered_CAA18`%) first-named authors could be classified as either men (n=`r male_count_CAA18`) or women (n=`r female_count_CAA18`). For CAA we generated a total of `r CAA_stm_topic_number` topics, with `r CAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. Three of these topics were associated with men, and three topics associated with women. Topics associated more with women include archives, GIS, geophysics, collaboration, and teaching. Topics associated more with men include environmental and landscape archaeology.

@@

Related work on gender differences in research topics has noted major differences in the proportions of men and women across many academic-related interests. One early and widely discussed theory, especially in psychology, to explain this is the theory of people-thing interest dimensions which proposes that men have stronger interest in things and their mechanisms, while women have a stronger interest in people and their feelings [@Miner1922; @su2009men]. @StoetGeary2022 used this theory in their investigation of gender differences in 473,260 adolescents’ aspirations to work in things-oriented (e.g., mechanic), people-oriented (e.g., nurse), and STEM (e.g., mathematician) careers across 80 countries and economic regions using data from the 2018 Programme for International Student Assessment (PISA). They found that boys generally aspired to a things-oriented or STEM occupation and  girls to a people-oriented occupation. Some of our results are consistent with this people-thing model, for example, 'people' topics such as burials, cemeteries, bodies, graves, collaboration, and teaching are associated more with women than men.

@@

A key limitation of this study is our concept of gender itself, and how we measure it. Like many social science studies, we have measured gender assuming it has two binary categories. However, we recognise that many cultures have long included more than two genders [@wilson1996we; @graham2004s], and there is a growing awareness of this in Western cultures also. A better measure of gender would represent it as a multifaceted spectrum [@tobin2010intrapsychics]. The problem with our binary measure is that it does not reflect our current understanding of gender, forces people in misclassified categories, and is hostile to public acceptance and advocacy for transgender and nonbinary individuals. Our instrument for collecting gender data only returns two categories, so this has limited potential for overcoming this limitation. To overcome this limitation, we recommend that conference organisers collect gender information directly from presenters using inclusive gender measures. For example, by providing nonbinary options for presenters on registration forms, and by asking about gender as an open‐ended question for participants to self-identify. We recommend that future work on gender in archaeology avoid 'othering' language when describing results. For example, reporting a sample as '150 participants (48% women; 49% men; 3% other)' violates ethical standards because such wording implies that binary gender is normal or appropriate, whereas trans and nonbinary gender is not (it is 'other'). Our hope is that our study might be the last one done by archaeologists to discuss gender as a binary.

@@

<!-- The following line inserts a page break  -->
\newpage

# References 
<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
<div id="refs"></div>

@@

The current Git commit details are:
u
```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

>>>>

---
title: "Correlations between gender and research topics at three major archaeology conferences"
author:
  - Yichun Chen:
      email: yichun33@uw.edu
      institute: [UofW]
      correspondence: true
  - Ben Marwick:
      email: bmarwick@uw.edu
      institute: [UofW]
      correspondence: false
institute:
  - UofW: Department of Anthropology, University of Washington, Seattle
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      number_sections: no
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
---

@@

Gender bias and imbalance has been a concern in archaeology since the earliest discussions of the social structure of the discipline [@Gero1983]. According to the American Anthropological Association's (AAA) *AnthroGuide*, there is a growing number of women participating in anthropology's graduate programs. For example, in the 2012-2013 school year, women consist of 64% of graduate students in anthropology programs and 65% of students that completed an anthropology doctoral degrees were women, whereas in 1972 32% of PhD are granted to women and 59% in 1995 [@bardolph2014critical]. Although women slightly outnumber men in anthropology graduate programs, previous work has shown substantial gender imbalances in publication practices in archaeology where men greatly outnumber women, especially as first authors in peer reviewed journal articles [@bardolph2014critical]. One of the first studies of this imbalance in publication practices is @bardolph2014critical, who looked at 7,381 members of the Society of American Archaeology and found 53% men and 47% women. She also looked at 1,601 articles published during 1990-2013 in five high-visibility archaeology journals and found a range of proportions of women to men authors of 0.32-0.73, with three of the five journals having a proportion of \<0.5.

@@

Another similar imbalance can be seen in terms of the authorship of articles or papers written. For example, for the authorship of the first authors of 1,104 articles published in the *Journal of Field Archaeology* during 1974--2018, 72% of them are men [@heath2020guest]. @heath2020guest investigates the possibility that the gender gap in authorship is due to due to sexism in the peer review process. Out of 830 instances of peer review for where both the reviewer's gender and the first author's gender could be determined, neither the first author's gender, the reviewer's gender, nor the combination of the two had a significant effect on the reviewer's recommendation.

@fulkerson2019dominates collected data on author's gender and occupational affiliation in peer reviewed journals (*American Antiquity* (AQ), *Advances in Archaeological Practice* (AAP), *Journal of California and Great Basin Anthropology* (JCGBA), and *California Archaeology* (CA)) and some non-peer-reviewed venues (the *SAA Archaeological Record* (SAA Record) and the SCA *Proceedings*). Among the 5,010 authors of 2,445 articles in their sample, 27.1% of first/single authors of peer-reviewed journal articles are women, and 72.9% are men. The gender gap is less pronounced in the non-peer-reviewed venues with women accounting for 40.8% of lead authors in 517 articles.

@@

When looking at gender ratios among the membership in Society for California Archaeology from 1967 to 2016, @tushingham2017peer report a trend of women increasingly maintaining their society membership they remain underrepresented in peer-reviewed journals. @tushingham2017peer examined authorship gender trends in 1,599 papers in three journals, *Journal of California and Great Basin Anthropology/Journal of California Archaeology* (JCGBA/JCA), *California Archaeology* (CA) and a non-peer reviewed *Proceedings* of the Society for California Archaeology (PSCA). In a total of 2,617 authors, 844 (32.3%) were women, 1,762 (67.3%) were men, and 11 (0.4%) were gender unknown/ambiguous [@tushingham2017peer]. They found significant increases in the proportion of female lead authors over time in JCGBA/JCA and PSCA, but not in CA, perhaps because of the shorter publishing period for this journal [@tushingham2017peer]. This similar trend of a gender gap in archaeology can also be seen in women's pay [@vanderwarker2018ucsb]. In the University of California, Santa Barbara Gender Equity Project, @vanderwarker2018ucsb report an imbalance in pay rates, for example, women make a greater proportion of people paid less \$60,000 and men outnumber women in salary brackets greater than \$60,000.

@@

```{r}
library(here)
library(tidyverse)
library(ggplot2)
# column names should be:
# session, FirstName, AbstractTitle

@@

A structural topic model (STM) allows us to include, alongside the typical topic modeling process, other document-level metadata to analyse covariance between topics and metadata [@roberts2019package]. Covariates of interest can be included into the prior distributions for document-topic proportions and topic-word distributions using a standard regression model [@roberts2014structural]. This means that we can examine the relationship between the topics and document-level variables of interest. In our case, we computed the relationship between the inferred the gender of the first-named presenter for each presentation, and the distribution of topics in that person's presentation. After we observed the topics for each presentation, we then generated a regression where the topic is the outcome variable, and gender is the explanatory variable. This regression gives us insights into whether there are non-random relationships between the inferred gender of an archaeologist and the topics of their presentation. Our data visualisations represent the estimated marginal effect (the x-axis values) of gender on each topic (distributed on the y-axis). Our visualisations show point estimates and 95% confidence intervals for each topic, and we interpret a statistically significant gender effect on the distribution of a topic when the 95% confidence interval does not include zero. We use triangular points and red colouring to indicate the significant effects, and black circular points for non-significant effects. Our plots include summaries each topic represented by the top 12 stemmed words for each topic.

# Reproducibility and open source materials {.unnumbered}

@@

```{r, eval=TRUE}

@@

@@

Overall we see similar women-to-men ratios for the SAA (`r female_to_male_SAA18`) and EAA (`r female_to_male_EAA18`), but much lower for the CAA (`r female_to_male_CAA18`) (Figure \@ref(fig:basic-viz)). Even before we look into the gender preferences for specific topics within each conference, we already have a hint that computational topics may be less preferred by women than by men.

```{r basic-viz}
#| fig.cap = "Frequencies of papers at each of the three conferences by gender"

# some basic visualisations to show the data
list_confs <- 
  list(SAA18_gender %>% 
              mutate(session = as.character(session)),
       CAA18_gender,
       EAA18_gender %>% 
              mutate(session = as.character(session))
       )

@@

all_conf_tbl <- 
  bind_rows(list_confs,
            .id = "conf") %>% 
  mutate(gender = ifelse(gender == "female",
                         "woman", "man"))

# how many papers per conf?
ggplot(all_conf_tbl) +
  aes(conf,
      fill = gender) +
  geom_bar(position = "dodge") +
  # colours from https://blog.datawrapper.de/gendercolor/
  scale_fill_discrete(type = c("#8625F5", "#1FC3AA")) +
  theme_minimal(base_size = 14) +
  theme(legend.position = c(.2,.60)) +
  labs(x = "", 
       y = "number of papers presented in 2018")
```

```{r saa-stm-plot}
#| fig.cap = "Point estimates and 95% confidence intervals for the estimated 
#| marginal effect of gender on each topic identified in titles of presentations at
#| 2018 SAA meeting"

# get plots
library(tidyverse)

SAA_stm_topic_number <-
  SAA18_stm_plot$model$settings$dim$K
SAA_stm_topic_number_significant_covary <- 
  nrow(ggplot2::layer_data(SAA18_stm_plot$plot, 3))
```

In the SAA data we found a total of `r prettyNum(SAA18_row, big.mark = ",")` presentations. Of these we could identify the first-named authors of `r count_gendered_SAA18` (`r perc_gendered_SAA18`%) presentations as either men (n=`r male_count_SAA18`) or women (n=`r female_count_SAA18`). In the SAA presentations we identified the optimum number of topics as `r SAA_stm_topic_number`, with `r SAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter (Figure \@ref(fig:saa-stm-plot)). Eight of these topics were associated with men, and nine topics associated with women. One of the main difference that we can see between the topics of the genders are the locations that the presenters are interested in. Topics associated more with women include bioarchaeology, cemeteries, burials, shells, and ceramics. Topics associated more with men include survey and landscape archaeology, geoarchaeology, rituals, and regional studies. Women are more likely to work on locations such as Mesoamerica, Arizona and national parks, while men are more likely to present on topics about the Great Lakes, and Honduras.

```{r eaa-stm-plot}
#| fig.cap = "Point estimates and 95% confidence intervals for the estimated 
#| marginal effect of gender on each topic identified in titles of presentations at
#| 2018 EAA meeting"

EAA_stm_topic_number <-
  EAA18_stm_plot$model$settings$dim$K
EAA_stm_topic_number_significant_covary <- 
  nrow(ggplot2::layer_data(EAA18_stm_plot$plot, 3))
```

For the EAA data we have `r prettyNum(EAA18_row, big.mark = ",")` presentations, and `r count_gendered_EAA18` (`r perc_gendered_EAA18`%) where the first author could be classified as either a man (n=`r male_count_EAA18`) or woman (n=`r female_count_EAA18`). For EAA we generated a total of `r EAA_stm_topic_number` topics, with `r EAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter (Figure \@ref(fig:eaa-stm-plot)). Seven of these topics were associated with men, and nine topics associated with women. Although topics significantly associated with men and women both include the word "Mediterranean", women seem to be focusing more on the western Mediterranean while men seems to be focusing on the northern Mediterranean. Topics associated more with women include burials, graves, museums, animals, diet, and ritual. Topics associated more with men include geoarchaeology, architecture, and towns.

```{r caa-stm-plot}
#| fig.cap = "Point estimates and 95% confidence intervals for the estimated 
#| marginal effect of gender on each topic identified in titles of presentations at
#| 2018 CAA meeting"

CAA_stm_topic_number <-
  CAA18_stm_plot$model$settings$dim$K
CAA_stm_topic_number_significant_covary <- 
  nrow(ggplot2::layer_data(CAA18_stm_plot$plot, 3))
```

For the CAA meeting we have `r prettyNum(CAA18_row, big.mark = ",")` presentations, and `r count_gendered_CAA18` (`r perc_gendered_CAA18`%) first-named authors could be classified as either men (n=`r male_count_CAA18`) or women (n=`r female_count_CAA18`). For CAA we generated a total of `r CAA_stm_topic_number` topics, with `r CAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter (Figure \@ref(fig:eaa-stm-plot)). Three of these topics were associated with men, and three topics associated with women. Topics associated more with women include archives, GIS, geophysics, collaboration, and teaching. Topics associated more with men include environmental and landscape archaeology.

@@

Related work on gender differences in research topics has noted major differences in the proportions of men and women across many academic-related interests. One early and widely discussed theory, especially in psychology, to explain this is the theory of people-thing interest dimensions which proposes that men have stronger interest in things and their mechanisms, while women have a stronger interest in people and their feelings [@Miner1922; @su2009men]. @StoetGeary2022 used this theory in their investigation of gender differences in 473,260 adolescents' aspirations to work in things-oriented (e.g., mechanic), people-oriented (e.g., nurse), and STEM (e.g., mathematician) careers across 80 countries and economic regions using data from the 2018 Programme for International Student Assessment (PISA). They found that boys generally aspired to a things-oriented or STEM occupation and girls to a people-oriented occupation. Some of our results are consistent with this people-thing model, for example, 'people' topics such as burials, cemeteries, bodies, graves, collaboration, and teaching are associated more with women than men.

@@

A key limitation of this study is our concept of gender itself, and how we measure it. Like many social science studies, we have measured gender assuming it has two binary categories. However, we recognise that many cultures have long included more than two genders [@wilson1996we; @graham2004s], and there is a growing awareness of this in Western cultures also. A better measure of gender would represent it as a multifaceted spectrum [@tobin2010intrapsychics]. The problem with our binary measure is that it does not reflect our current understanding of gender, forces people in mis-classified categories, and is hostile to public acceptance and advocacy for transgender and nonbinary individuals. Our instrument for collecting gender data only returns two categories, so this has limited potential for overcoming this limitation. To overcome this limitation, we recommend that conference organisers collect gender information directly from presenters using inclusive gender measures. For example, by providing nonbinary options for presenters on registration forms, and by asking about gender as an open‐ended question for participants to self-identify. We recommend that future work on gender in archaeology avoid 'othering' language when describing results. For example, reporting a sample as '150 participants (48% women; 49% men; 3% other)' violates ethical standards because such wording implies that binary gender is normal or appropriate, whereas trans and nonbinary gender is not (it is 'other'). Our hope is that our study might be the last one done by archaeologists to discuss gender as a binary.

@@

<!-- The following line inserts a page break  -->

# References

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

::: {#refs}
:::

@@

The current Git commit details are: u

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
